---
title: "Generalized Marginal Models and Generalized Mixed-effects Models"
author: "Hana Akbarnejad"
date: "5/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(gee)
library(lme4)
library(nlme)
library(tidyverse)
library(readxl)

health_data = read_excel("HW8-HEALTH.xlsx") %>% 
  janitor::clean_names() %>% 
  mutate(
    health = as.factor(health),
    agegroup = as.factor(agegroup),
    id = factor(id),
    good_base = ifelse(health == "Good", 1, 0)
  )
```

**response: participants' self-rated "health": Binary (Good/Poor)**

(a) Evaluate the bivariate, cross-sectional relationship between random-ized group assignment and participants health self-rating at the time of ran-domization. Interpret and discuss these findings.

```{r}

data_baseline = health_data %>% 
  filter(time == 1)

base_glm = glm(health ~ txt, data = data_baseline, family = "binomial")
summary(base_glm)
```

p-value = 0.49 > 0.05 we fail to reject null and conclude that there is no significant relationship between health status and the group they are assigned to (That is why is "randomized").

(b) Perform a longitudinal data analysis across all study follow-up visits (but not at randomization) to describe the relationship of the participants self-ratings as a function of the effects of health self-rating at the baseline, treatment group, month post randomization, and age group as predictors. Fit a GEE with unstructured correlation structure. Interpret your results.

```{r}

data_gee = health_data %>% 
  filter(
    time >1
  )
#   
# health_gee = gee(health ~ agegroup + good_base + txt + time, data = data_gee, family = "binomial", id=id, corstr = "unstructured", scale.fix= FALSE)
```

